Estimating duration using survival analysis

### 2023-09-20 cis-perfect-testing.tex
Minor editing attempt

The observations of detected episode $i$'s are fully characterised by the time of the negative prior to the episode, $t_{i,1}$, the time of the negative following the episode, $t_{i,2}$, and the test schedule of the individual in which it occurs, $\sched_i$.
$t_{i,1}$ and $t_{i,2}$ are deterministic functions of $\tilde{y}_i$.
Specifically, $t_{i,1} = \tbefore_{\sched_i}(b_i)$ and $t_{i,2} = \tbefore_{\sched_i}(e_i)$.
Let $y_i = (t_{i,1}, t_{i,2}, \sched_i)$.
The possible values of $y_i$ require that $t_{i,1}$ and $t_{i,2}$ both appear in the test schedule $\sched_i$, and that there is a positive test between them.
Formally, this set of possible values is $\mathbb{D} = \{ (t_{i,1}, t_{i,2}, \sched_i) : t_{i,1} \in \sched_i \wedge t_{i,2} \in \sched_i \wedge \tafter_{\sched_i}(t_{i,1}) < t_{i,2} \}$.

@@

Undetected (or excluded) episodes have a start time before the individual's first test, an end time after their last test, or began and ended between tests.
Formally, define undetected episodes as $\mathbb{U} = \{ (b_i, e_i, \sched_i) : b_i \leq \min(\sched_i) \vee e_i \geq \max(\sched_i) \vee e_i < \tafter_{\sched_i}(b_i) \}$.
Denote by $n_u$ the unknown number of undetected episodes which I will treat as missing data.

@@

Due to the censoring and missed infections, the observations of episodes are incomplete.
The observations are equivalent to counts of the number of episodes in each set $\mathbb{A}_{\vec{d}}$, $n_{\vec{d}}$.
Additionally, I will impute the total number of episodes (including undetected episodes) $n_u$.
Let $n = n_u + \sum_{\vec{d} \in \mathbb{D}} n_{\vec{d}}$.
For any infection episode, consider the probability of it being in each set $\mathbb{A}_{\vec{d}}$ or $\mathbb{U}$.
\begin{align}
  p_{\vec{d}} 
  &= \prob(\tilde{y}_i \in \mathbb{A}_{\vec{d}}) \\
  &= \sum_{(b, e, \sched) \in \mathbb{A}_{\vec{d}}} \prob(\tilde{y}_i = (b, e, \sched)) \\
  p_U
  &= \prob(\tilde{y}_i \in \mathbb{U}) \\
  &= \sum_{(b, e, \sched) \in \mathbb{U}} \prob(\tilde{y}_i = (b, e, \sched))
\end{align}

>>>>

The observations of detected episode $i$'s are fully characterised by the time of the negative prior to the episode, $t_{i,1}$, the time of the final positive in the episode, $t_{i,2}$, and the test schedule of the individual in which it occurs, $\sched_i$.
$t_{i,1}$ and $t_{i,2}$ are deterministic functions of $\tilde{y}_i$.
Specifically, $t_{i,1} = \tbefore_{\sched_i}(b_i)$ and $t_{i,2} = \tbefore_{\sched_i}(e_i+1)$ where $\tbefore_{\sched}(t) = \max \{ t' \in \sched \ssep t' < t \}$ is the test immediately before time $t$.
Let $y_i = (t_{i,1}, t_{i,2}, \sched_i)$.
The possible values of $y_i$ require that $t_{i,1}$ and $t_{i,2}$ both appear in the test schedule $\sched_i$, and that there is a positive test between them.
Formally, this set of possible values is $\mathbb{D} = \{ (t_{i,1}, t_{i,2}, \sched_i) : t_{i,1} \in \sched_i \wedge t_{i,2} \in \sched_i \wedge \tafter_{\sched_i}(t_{i,1}) < t_{i,2} \}$, where $\tafter_{\sched}(t) = \min\{ t' \in \sched \ssep t' > t \}$ is the next test at or after time $t$.

@@

Undetected (or excluded) episodes have a start time before the individual's first test, an end time after their last test, or began and ended between tests.
Formally, define undetected episodes as $\mathbb{U} = \{ (b_i, e_i, \sched_i) : b_i \leq e_i \left( b_i \leq \min(\sched_i) \vee e_i \geq \max(\sched_i) \vee e_i < \tafter_{\sched_i}(b_i) \right) \}$.
Denote by $n_u$ the unknown number of undetected episodes which I will treat as missing data.

@@

Due to the censoring and missed infections, the observations of episodes are incomplete.
The observations are equivalent to counts of the number of episodes in each set $\mathbb{A}_{\vec{d}}$, $n_{\vec{d}}$.
Additionally, I will impute the total number of episodes (including undetected episodes) $n_u$.
Let $n = n_u + \sum_{\vec{d} \in \mathbb{D}} n_{\vec{d}}$.
For any infection episode, consider the probability of it being in each set $\mathbb{A}_{\vec{d}}$ or $\mathbb{U}$.
\begin{align}
  p_{\vec{d}} 
  &= \prob(\tilde{y}_i \in \mathbb{A}_{\vec{d}} \mid \theta) \\
  &= \sum_{(b, e, \sched) \in \mathbb{A}_{\vec{d}}} \prob(\tilde{y}_i = (b, e, \sched) \mid \theta) \\
  p_U
  &= \prob(\tilde{y}_i \in \mathbb{U} \mid \theta) \\
  &= \sum_{(b, e, \sched) \in \mathbb{U}} \prob(\tilde{y}_i = (b, e, \sched) \mid \theta)
\end{align}
